Visual inference for networks

### 2016-02-04 paper/network-inference.Rnw
reference added
copied the list into the paper

@@

Citing happens only with cite - like this~\cite{buja:2009}. Footnotes are ok%
\footnote{Footnotes appear at the bottom of the column}.

>>>>

\begin{enumerate}
\item Need to complete lineups in 2-3 weeks
\item Lineups: 
  \begin{enumerate}
  \item What sizes? 3, 6, 9, 12
  \item What data? Football, olga's data, teenage friends data?
  \item Other things to consider: coloring of nodes? 
  \end{enumerate}
\item Get simulated networds from models from RSiena
\item Figure out another way to fit a model and then simulate from it? 
\end{enumerate}

Possible section outline for paper:
\begin{enumerate}
\item Introduction - visual inference, networks
\item Data and Model fitting \& simulation
\item Lineup methods
\item Results
\item Conclusions and Discussion
\end{enumerate}

@@

Citing happens only with cite - like this for the lineup protocol~\cite{buja:2009}, and for RSiena~\cite{RSiena}. Footnotes are ok%
\footnote{Footnotes appear at the bottom of the column}.
